### 2024-09-14 Response/Response.tex

\underline{Authors' Reply}: Lines 4 to 17 of the MGW algorithm can be indeed run simultaneously. The algorithm does not require any information about the output of the subtasks' executions in order to execute these lines. In fact, it only requires the sizes of inputs and outputs of each subtask which are given by the task call graph. We have added the following sentences in Section IV of the revised manuscript to better clarify this fact.\\

\begin{my}{1cm}{1cm}
	\rev{Note that in order to calculate the weights of subtasks, there is no need to actually execute them. The only required information is the size of input and output of each subtask which is already known from the task call graph. Thus, Lines 4 to 17 of the MGW algorithm can be run simultaneously.\newline}
\end{my}

\item \underline{Reviewer's Comment}: \textit {``No theoretical guarantee for the energy consumption of the proposed algorithm was provided in this paper. What is the approximation ratio of the proposed algorithm? Theoretical analysis should be provided.''\newline}

\underline{Authors' Reply}: 
It should be noted that S-ETEM problem achieves the optimal solution of the original ET's energy minimization (ETEM) problem. Furthermore, DS-ETEM problem can achieve the optimal solution with no approximation. In particular, the ETEM problem has been transformed into S-ETEM problem. These two problems are equivalent and can achieve the same optimal solution. This has been achieved by converting the many-to-one matching into a one-to-one matching by introducing the concept of virtual resources. In order to further decompose the ETEM problem and eliminate the dependency of constraint (\ref{eq9}), we have introduced the parameter $\beta_{v_d^u}$. By determining the optimal value of $\beta_{v_d^u}$, the optimal energy can be obtained and there would not be any approximation when solving the problem. Please note that determining the optimal value of $\beta_{v_d^u}$ is beyond the scope of our work and is considered for future works. However, there are approaches to calculate it iteratively such as the one given in \cite{b2}. In order to address the reviewer's comment, we have revised the manuscript and further clarified the derivation of ETEM and S-ETEM problems and the role of $\beta_{v_d^u}$.\\

\begin{my}{1cm}{1cm}
	\rev{
	To leverage the matching algorithm, we need to calculate the cost of each matching between subtasks and computing resources. To accomplish this, we first transform the ETEM problem into an equivalent simplified problem. We then show that the transformed problem is decomposable, and the resultant decomposed problems are still equivalent to the ETEM problem. \newline

	$\cdots$

	It is also worth noting that for a given $\beta_{v_d^u}$, by solving S-ETEM, we can achieve the optimal solution of the ETEM problem. In other words, by determining the optimal value of $\beta_{v_d^u}$ for each $d\in\mathcal{D}^u$ and $u\in\mathcal{U}$, the optimal ET's transmitted energy can be obtained and there would not be any approximation.\\
}
\end{my}

We have also added the following explanation in the footnote of Page 10.\newline

\begin{my}{1cm}{1cm}
	\rev{
		For the case of non-optimal $\beta_{v_d^u}$, one needs to analyze the approximation ratio of the proposed algorithm. An approach similar to \cite{b2} can be followed. However, we leave this extension as future work.\newline
	}
\end{my}

\item \underline{Reviewer's Comment}: \textit {``In the experiments, only two WDs were deployed in the network. And the dependencies of subtasks generated by each WD were not provided in the experiments. Besides, the authors only evaluated the impact of CPU cycles for WDs on algorithm performance, which is not enough.''} \newline

\underline{Authors' Reply}: To address the reviewer's comment, we have included more simulation results in the revised manuscript. First, we have considered a scenario with 200 WDs and included Figs. \ref{fig:10a} and \ref{fig:10b} that show ET’s transmitted energy for WiEnTM and two baseline schemes. As suggested by the reviewer, in Fig. \ref{fig:10a}, we vary the task's total internal input and output bits, while in Fig. \ref{fig:10b}, we evaluate the effect of total CPU cycles on energy consumption. In addition, we have included Figs. \ref{fig:7arr} and \ref{fig:7brr} that evaluate the effect of both the total number of CPU cycles and the total internal input/output bits of the task on ET's transmitted energy for WiEnTM in comparison to the offloading algorithm in \cite{b13}. We have included the following explanations in Section V of the revised manuscript.\\

\setcounter{figure}{7}
\begin{figure}
	\centering
	\begin{subfigure}[b]{.43\textwidth}
		\centering
		\includegraphics[width=\linewidth]{simulation2_a.pdf}
		\caption{} \label{fig:7arr}
	\end{subfigure}
	\begin{subfigure}[b]{.43\textwidth}
		\centering
		\includegraphics[width=\linewidth]{simulation2_b.pdf}
		\caption{} \label{fig:7brr}
	\end{subfigure}

	\caption{\textcolor{blue}{Comparison of ET's transmitted energy between WiEnTM and the algorithm proposed in \cite{b13} for different a) task's CPU cycles (i.e., $\sum_{v_d\in\mathcal{V}_d}C_{v_d}$) and, b) task's internal input/output bits (i.e., $\sum_{v_d^i,v_d^j\in\mathcal{V}_d}N_{v_d^i,v_d^j}$).}} \label{fig:7rr}
\end{figure}

\begin{figure}
	\centering
	\begin{subfigure}[b]{.24\textwidth}
		\centering
		\includegraphics[height=1.2\linewidth]{simulation3_a.pdf}
		\caption{} \label{fig:10a}
	\end{subfigure}
	\begin{subfigure}[b]{.24\textwidth}
		\centering
		\includegraphics[height=1.2\linewidth]{simulation3_b.pdf}
		\caption{} \label{fig:10b}
	\end{subfigure}

	\caption{\textcolor{blue}{Comparison of ET's transmitted energy for three offloading policies when there are 200 WDs. 1) Local computation only, 2) computation offloading only, and 3) WiEnTM algorithm.}} \label{fig:10}
\end{figure}

\begin{my}{1cm}{1cm}
	\rev{
	We further investigate the performance of our proposed WiEnTM algorithm by evaluating the ET's transmitted energy in comparison to that of \cite{b13}. Figs. \ref{fig:7arr} and \ref{fig:7brr} illustrate the effect of the task's CPU cycles and the task size (i.e., the number of input/output bits), respectively. The results show that by using WiEnTM, the ET consumes up to $34\%$ less energy compared to the algorithm in \cite{b13}.

	$\cdots$

	We now consider 200 WDs and investigate the ET transmission energy required to enable WDs execute their tasks. We study three different policies: 1) Local computing, 3) computation offloading, and 3) WiEnTM algorithm. We assume that among these devices, 100 WDs have a task with the call graph shown in Fig. \ref{fig:5a} and the rest with the task call graph of Fig. \ref{fig:5b}.

		$\cdots$

	Fig. \ref{fig:10a} shows the ET's energy transmission when we vary the task's total CPU cycles. Additionally, Fig. \ref{fig:10b} illustrates the ET's energy for different numbers of the task's total  input/output bits, which reflect the size of the tasks.

		$\cdots$

	In particular, according to Fig. \ref{fig:10a}, comparing to the local computing case, a higher improvement is obtained for the computationally intensive tasks.

		$\cdots$

	The results of Fig. \ref{fig:10b} imply that WiEnTM mainly follows the policy of offloading to edge/cloud server for tasks with a small number of input/output bits. As we increase the number of bits, the algorithm tends to rely more on local computing. As can be observed, WiEnTM greatly outperforms both schemes.
	}\newline
\end{my}

Furthermore, the dependencies between subtasks of each WD are shown in Fig. \ref{fig:5}. We have included the following sentences in Section V of the revised manuscript to further clarify this issue.\newline

\begin{my}{1cm}{1cm}
	\rev{
		These figures show the dependencies in the task call graph of each WD. An arrow leaving node $i$ toward $j$ indicates that subtask $j$ is dependent on subtask $i$.
	}\newline
\end{my}

\end{enumerate}

We would like to gratefully thank the reviewer for the valuable comments and suggestions. We hope that we have addressed these comments satisfactorily.\newline

\section{Response to Reviewer 4}
\begin{enumerate}

	\item \underline{Reviewer's Comment}: \textit{````an'' MEC rather than ``a'' MEC;''} \newline

	\underline{Authors' Reply}: We have applied the reviewer's comment throughout the paper and updated the manuscript.\\

	\item \underline{Reviewer's Comment}: \textit{``This paper considers half-duplex transmission for WDs, where computation offloading cannot be performed simultaneously with energy harvesting. How about the full-duplex?''} \newline

	\underline{Authors' Reply}: Inspired by \cite{b2,b10,b11,b14}, in our work, we consider half-duplex transmission for WDs. Due to the production costs, battery-less devices usually lack a full-duplex transceiver. In the case that devices are equipped with full-duplex transceivers, we do not need a harvest-then-offload mechanism as both offloading and energy harvesting can be done simultaneously. There are several works studying simultaneous wireless information and power transfer (SWIPT) \cite{b8} for devices with full-duplex transmission. However, this is beyond the scope of our work and is considered for future works. We have added the following explanations to Section II of the revised manuscript. \newline

	\begin{my}{1cm}{1cm}
		\rev{
			In contrast, for the case of full-duplex transmission, scheduling algorithms are categorized as the simultaneous wireless information and power transfer (SWIPT) \cite{b8} mode. However, considering the constraints of the production costs and devices' form factor for battery-less WDs, they usually lack a full-duplex transceiver to perform energy harvesting and data transmission simultaneously.
		}\newline
	\end{my}

	We have also added the following sentence to Section VI of the revised manuscript.

	\begin{my}{1cm}{1cm}
		\rev{
				We will also study more powerful WDs with full-duplex capability in future.
		}\newline
	\end{my}

	\item \underline{Reviewer's Comment}: \textit{``The font size in Fig. 2 should be adjusted. For example, the font is too large for ``WET''.''} \newline

	\underline{Authors' Reply}: We have adjusted the font size of Fig. \ref{fig2r} as suggested. \newline

	\renewcommand{\figurename}{Fig.}
	\renewcommand{\thefigure}{2}
	\begin{my}{1cm}{1cm}
		\rev{
			\begin{figure}[h!]
				\centering
				\includegraphics[height=95pt]{TDMA.pdf}
				\caption{\textcolor{blue}{Harvest-then-offload scheduling with TDMA protocol for a system of two WDs. An episode of length $\Gamma$ is divided into two times frames of WET and offloading/local computing. In the case of offloading, the offloading/local computing time frame consists of three slots. The first and last slots are for transmitting the data and retrieving the results, respectively. The second slot is dedicated to the computation in the MEC server or transmission to/from the cloud server.}}\label{fig2r}
			\end{figure}
		}
	\end{my}

	\item \underline{Reviewer's Comment}: \textit{``The authors state that “the partial offloading provides a more realistic model of tasks”. It is suggested to provide more explanation.''}\newline

	\underline{Authors' Reply}: In the partial offloading model, each task is represented by its call stack which exactly maps to a real computer program. Note that binary offloading is a special case of partial offloading when we only consider a single partition. To further clarify this issue, we have included the following explanation in Section II of the revised manuscript.\newline

	\begin{my}{1cm}{1cm}
		\rev{
			The partial offloading provides a more realistic model of tasks as it leverages the task call graph to represent each task. This accurately models the call stack of a computer program.\newline
		}
	\end{my}

	We have also provided an application example in the footnote of Page 3 as below.\newline

	\begin{my}{1cm}{1cm}
		\rev{
			\textcolor{blue}{For instance, \textit{Pyan}\cite{b41} is a Python module that generates the task call graph of a Python code by analysis of its modules and functions.}\newline
		}
	\end{my}

	\item \underline{Reviewer's Comment}: \textit{``Why ``the cumulative energy consumption of the devices is no more than their harvested energy''? could you please give a realistic example to illustrate the assumption?''}\newline

	\underline{Authors' Reply}: Indeed, the cumulative energy consumption of devices must be no more than their harvested energy. It is because we consider wireless-powered devices which cannot store energy for later use. Thus, the devices cannot use more energy than the harvested amount. It also ensures the sustainable operation of the devices. The same assumption has been made in similar works \cite{b10,b30,b13,b39,b26,b2}. We have included the following sentences in Section II of the revised manuscript to make this fact more clear.\newline

	\begin{my}{1cm}{1cm}
		\rev{
			As described earlier, we assume sustainable operation of WDs by only relying on the harvested energy (i.e., battery-less network). Thus, the cumulative energy consumption of the devices on each episode must be no more than their harvested energy.\\
		}
	\end{my}

	\item \underline{Reviewer's Comment}: \textit{``More recent and important references are required.''}\newline

	\underline{Authors' Reply}: To address the reviewer's comment, we have removed a few of outdated references and cited five recently published papers as follows. \newline
	\begin{my}{1cm}{1cm}
		\rev{
	{\small
		\noindent\cite{b35} Y. Yu, Y. Yan, S. Li, and D. Wu, ``Task delay minimization in wireless powered mobile edge computing networks: A deep reinforcement learning approach,'' in \textit{Proc. of Int. Conf. Wireless Commun. Signal Process. (WCSP)}, Changsha, China, Mar. 2021.\\[10pt]
		\cite{b38} Y. Li, Y. Wu, M. Dai, B. Lin, W. Jia, and X. Shen, ``Hybrid NOMA-FDMA assisted dual computation offloading: A latency minimization approach,'' \textit{IEEE Trans. Netw. Sci. Eng.}, vol. 9, no. 5, pp. 3345--3360, Sep. 2022.\\[10pt]
		\cite{b37} K. Guo, M. Yang, Y. Zhang, and J. Cao, ``Joint computation offloading and bandwidth assignment in cloud-assisted edge computing,'' \textit{IEEE Trans. Cloud Comput.}, vol. 10, no. 1, pp. 451--460, Mar. 2022.\\[10pt]
		\cite{b39} R. Zhang and C. Zhou, ``A computation task offloading scheme based on mobile-cloud and edge computing for WBANs,'' in \textit{Proc. of IEEE Int. Conf.	Commun. (ICC)}, Seoul, Korea, Repulic of, Mar. 2022.\\[10pt]
		\cite{b40} Z. Gao, W. Hao, and S. Yang, ``Joint offloading and resource allocation for multi-user multi-edge collaborative computing system,'' \textit{IEEE Trans. Veh. Technol.}, vol. 71, no. 3, pp. 3383--3388, Mar. 2022.}\\}
	\end{my}

	We have also cited these works in the following sentences in Section I of the revised manuscript.\\

	\begin{my}{1cm}{1cm}
		\rev{
			Mobile edge computing (MEC) is a state-of-the-art computation paradigm to address the challenge of insufficient computing resources in Internet of Things (IoT) networks \cite{b35, b4}. By deploying the edge servers, nearby devices can offload their computation tasks. Dispatching those tasks that require a higher amount of energy will let devices save more energy \cite{b38}. However, as the computation tasks become more and more intensive, a coordination with cloud servers might be inevitable \cite{b37}. As a result, three-tier models consisting of cloud, edge, and IoT devices are introduced to overcome the aforementioned challenges \cite{b5,b6,b39,b40}.

			$\cdots$

			In the existing work \cite{b39}, authors proposed a scheme that aims to minimize the total cost in terms of energy and delay for a three-tier cloud-edge-IoT system. Gao \textit{et al.} in \cite{b40} proposed an offloading algorithm to minimize an objective called the energy time cost (ETC) for a three-tier network. Although \cite{b5}, \cite{b39}, and \cite{b40} all benefit from a computationally-scalable three-tier system, IoT devices still rely on battery energy and they thus lack the sustainability feature of WPMEC systems.
			\\}
	\end{my}

\end{enumerate}

We would like to gratefully thank the reviewer for the valuable comments and suggestions. We hope that we have satisfactorily addressed these comments.\newline

\end{document}

### 2024-09-16 Response_V0.1/Response.tex

\section{Introduction}

Mobile edge computing (MEC) \cite{mao2017survey} has emerged as a promising technological solution to overcome the challenges faced by mobile devices (MDs) when performing high computational tasks, such as real-time data processing and artificial intelligence applications \cite{zhou2019edge} \cite{yousefpour2019all}. In spite of the MDs' technological advancements, their limited computing power and battery may lead to task drops, processing delays, and an overall poor user experience. By offloading intensive tasks to nearby edge nodes (ENs), MEC effectively empowers computation capability and reduces the delay and energy consumption. This improvement enhances the users' QoE, especially for time-sensitive computation tasks \cite{TNSE-QOE-24} \cite{ shah2018hierarchical}.

Efficient task offloading in MEC is a complex optimization challenge due to the dynamic nature of the network and the variety of MDs and servers involved \cite{jiang2019toward} \cite{TNSE-WU-24}. In particular, determining the optimal offloading strategy, scheduling the tasks, and selecting the most suitable EN for task offloading are the main challenges that demand careful consideration. Furthermore, the uncertain requirements and sensitive latency properties of computation tasks pose nontrivial challenges that can significantly impact the computation offloading performance in MEC systems with limited resources.

\textcolor{blue}{To cope with the dynamic nature of the network, recent research has proposed several task offloading algorithms using machine learning methods. In particular, reinforcement learning (RL) hold promises to determine optimal decision-making policies by capturing the dynamics of environments and learning strategies for accomplishing long-term objectives \cite{arulkumaran2017deep}. RL can effectively tackle the challenges of MEC arising from the ever-changing nature of networks, MDs, and servers' heterogeneity. This ultimately improves the MD users' QoE. We explore state-of-the-art RL-based techniques characteristic to discuss how they address task offloading problems in MEC. To minimize energy consumption, Munir \textit{et al.} \cite{munir2021multi} developed a semi-distributed approach using a multi-agent RL (MARL) framework for self-powered MEC. Gong \textit{et al.} in \cite{gong2022edge} proposed a DRL-based network structure in the industrial IoT (IIoT) systems to jointly optimize task offloading and resource allocation to achieve lower energy consumption and decreased task delay. To investigate privacy aware computation offloading problem, Wu \textit{et al.} in \cite{wu2024combining} proposed a deep Q-network (DQN)-based method. They transform the problem on MDP to optimize computation rate and energy consumption in a queuing-based IIoT network. Sun \textit{et al.} in \cite{sun2024hierarchical} explored both computation offloading and service caching problems in MEC. They formulated an optimization problem that aims to minimize the long-term average service delay. They then proposed a hierarchical DRL framework, which effectively handles both problems under heterogeneous resources.}

%Researchers have recently proposed several task offloading algorithms to tackle the aforementioned issues. Mao \textit{et al.} in \cite{mao2016dynamic} introduced a computation offloading algorithm for MEC systems. This scheme aims to reduce the MD's energy consumption while meeting the computation delay constraints. In \cite{zhang2016energy}, Zhang \textit{et al.} proposed an offloading scheme for MEC in heterogeneous cellular networks, taking into account the energy-constrained MEC scenario and the heterogeneity of MDs when optimizing the offloading decisions. Bi \textit{et al.} in \cite{bi2018computation} proposed an algorithm to optimize decision-making about computation offloading and power transferring in a wireless-powered MEC. Ning \textit{et al.} in \cite{ning2018cooperative} introduced a heuristic algorithm designed to enhance the efficiency of the partial computation offloading model. The works in \cite{mao2016dynamic}-\cite{ning2018cooperative} primarily focus on quasi-static systems and are not well-suited for dynamic systems and time-varying conditions.

@@

%presents a more challenging problem. The impact of processing deadlines on the dynamic workload at the ENs influences the delay experienced by the offloaded tasks.

%In \cite{mao2016dynamic,zhang2016energy,bi2018computation,ning2018cooperative}, the processing capacity assigned to each MD by an EN remained unaffected by the number of offloaded tasks, resulting in a heavy load on the EN when a significant number of MDs offload their tasks to it. This heavy load can cause significant processing delays and even lead to missed deadlines and dropped tasks. To mitigate this issue, some existing works have proposed task offloading algorithms that consider the workloads at the ENs. In \cite{chen2018task}, Chen \textit{et al.} proposed an algorithm for task offloading in a software-defined ultra-dense network. The goal of this algorithm is to minimize task delay by formulating the task offloading scheme as a mixed integer non-linear program problem. Shah-Mansouri \textit{et al.} in \cite{shah2018hierarchical} proposed a QoE maximization slotwork for offloading decisions based on computation energy and delay reduction. They formulated a potential game to model competition among IoT users and achieved a close-to-optimal social cost.

\subsection{Related Work}
%\textcolor{black}{We explore state-of-the-art techniques characteristic to discuss how they address task offloading problems in scenarios that need to process massive data with limited devices in MEC, such as the Internet of Things (IoT), Internet of Vehicles (IoV), and Industrial IoT (IIoT)  environment.

	%Internet of Things (IoT) \cite{dai2020edge}, \cite{liao2023online}, \cite{Bolourian-WCL24}, 
	%Internet of Vehicles (IoV) \cite{Bolourian-WCL24}, 
	%and Industrial IoT (IIoT)  environment \cite{gong2022edge}, \cite{wu2023multi}, \cite{wu2024combining}

	%\subsubsection{DRL-Based Task Offloading Optimization in MEC}

	\textcolor{blue}{
		In recent years, edge computing has become a popular method for scenarios that need to process massive data with weak devices, such as IoTs \cite{zhang2023multi}, Internet of Vehicles (IoVs) \cite{lin2022multi}, \cite{wei2023many}, and Industrial IoT (IIoT) \cite{yuan2023adaptive} environment. To take advantage of RL methods for online computation offloading in MEC, Huang \textit{et al.} in \cite{huang2019deep}, focused on a wireless-powered MEC. They proposed a DRL-based approach, capable of attaining near-optimal decisions. This is achieved by selectively considering a compact subset of candidate actions in each iteration. Liu \textit{et al.} in \cite{liu2021learn} investigated a two-timescale computing offloading and resource allocation problem and proposed a resource coordination algorithm based on multi-agent DRL (MADRL), which can generate interactive information along with resource decisions. Zhou \textit{et al.} in \cite{zhou2021deep} used an MDP to model the interactions of the environment. They proposed a Q-learning approach to achieve optimal resource allocation strategies and computation offloading. Liao \textit{et al.} in \cite{liao2023online} introduced a double DRL algorithm for performing online computation offloading in MEC. This algorithm optimizes transmission power and scheduling of CPU frequency when minimizing both task computation delay and energy consumption. }

	\textcolor{blue}{
		In these researches authors investigated simple MEC networks and explored computation offloading problems, mainly focused on delay-tolerant tasks or single MEC network model, and did not take into account the challenges of dynamic network environment with the variety of MDs and servers involved. In actual scenarios, an MEC system can provide delay-constrained services for serval MDs and ENs at the same time, while the works \cite{huang2019deep}, \cite{liu2021learn} not consider delay-sensitive tasks for network model and \cite{zhou2021deep}, \cite{liao2023online} just considered the situation of a single server or user in the MEC system.}

	\textcolor{blue}{  
		In fact, the state of MD's computing and transmission power, arrived task's requirement, the energy state of MDs, and workloads at ENs all change dynamically with time in actual systems, thus a more realistic MEC scenario is needed. Besides the works \cite{huang2019deep}--\cite{liao2023online}, Wu \textit{et al.} in \cite{wu2023computation} introduced a stochastic game-based resource allocation in the SDN-based MEC network. They used an MDP and proposed a MARL method to minimize both energy consumption and processing delay. Dai \textit{et al.} in \cite{dai2020edge} introduced the integration of action refinement into DRL and designed an algorithm to concurrently optimize resource allocation and computation offloading. To optimize privacy protection and quality of service, authors in \cite{wu2024privacy} investigated the joint computation offloading and power allocation problems for the IIoT network. They modeled the problem as an MDP and proposed a multi-agent DDQN-based algorithm.
		In \cite{zhao2019deep}, Zhao \textit{et al.} proposed a computation offloading algorithm based on DRL, which addresses the competition for wireless channels to optimize long-term downlink utility. In this approach, each MD requires quality-of-service information from other MDs.}

	%In these researchs authours mostly investigated MEC networks and explored computation offloading problem, but in some works such as \cite{zhou2021deep} \cite{liao2023online} have mainly focused on single MEC network model, and has not taken into account the challenges of dynamic network environment with multiple ENs. In fact, the channel quality, requested task, and energy state on an MDs all change dynamically with time in an actual MEC scenario, thus a more realistic MEC scenario is needed, involving delay-sensitive tasks with processing deadlines in multiple MDs and ENs, which poses a more intricate challenge.

	\textcolor{blue}{
		While studies like \cite{wu2023computation}--\cite{zhao2019deep} explored task offloading problems in a more advanced scenario and proposed some DRL-based algorithms, MEC systems often encounter challenges related to managing time-varying resource requests from heterogeneous devices, imposing significant challenges in resource accessibility and overall system performance. To address this issue, the authors applied queuing theory to model MEC systems more accurately, reflecting real-world scenarios. 
		%\subsubsection{Queuing Theory for Computation Offloading}
		In \cite{Bolourian-WCL24}, the authors proposed an offloading algorithm using deep Q-learning for wireless-powered IoT devices in MEC systems. This algorithm aims to minimize the task drop rate while the devices solely rely on harvested energy for operation. Tang \textit{et al.} in \cite{9253665} investigated the task offloading problem for indivisible and deadline-constrained computational tasks in MEC systems. The authors proposed a distributed DRL-based offloading algorithm designed to handle uncertain workload dynamics at the ENs. 
		In \cite{huang2021deadline}, Huang \textit{et al.} proposed a DRL-based method based on a partially observable MDP (POMDP), which guarantees the deadlines of real-time tasks while minimizing the total energy consumption of MDs. This algorithm effectively tackles the challenges of dynamic resource allocation in large-scale heterogeneous networks. To optimize delay and energy consumption in an MEC-based IIoT system, Wu \textit{et al.} in \cite{wu2023multi} proposed a multi-agent DQN-based method based on POMDP to address computation offloading problem. In \cite{gao2022large}, Gao \textit{et al.} introduced an attention-based multi-agent algorithm designed for decentralized computation offloading.}

	\begin{table*}[htbp]\textcolor{blue}{
		\renewcommand{\arraystretch}{0.6}
		\captionsetup{name=TABLE}
		\caption{Comparison of Related Works Characteristic\vspace{4mm}}
		\scalebox{0.7}{%
			\begin{tabular}{ lp{3.4cm}p{4.5cm}p{5.2cm}p{1.7cm}p{3cm}p{4.6cm}l} 
				\toprule
				\textbf{Paper} & \textbf{Scenario} &  \textbf{Problem} &  \textbf{Objective} &  \textbf{Model} & \textbf{Method} &  \textbf{Drawbacks}  \\ \midrule
				\cite{liao2023online} & Queuing-based MEC & Online computation offloading & Minimize computation delay and energy consumption & MDP & DDQN & Only for a singel MEC system model  \\\midrule
				\cite{zhou2021deep} & heterogeneous MEC & Resource allocation and computation offloading & Minimize energy consumption of the entire system & MDP & DDQN & Only for a singel MEC system model \\\midrule				
				\cite{huang2019deep} & Wireless-powered MEC & Computation offloading and resource allocations & Maximize computation rate & MIP & DQN & Not consider delay-sensitive tasks \\\midrule
				\cite{wu2024privacy} & MEC-based IIoT  & Joint power allocation and computation offloading  & Optimization of privacy protection and quality of service. & MDP & Multi-agent DDPG & Not take user's deman into consideration \\\midrule
				\cite{zhao2019deep} & MEC & User association and resource allocation & Optimize downlink utility & MDP & Multi-agent D3QN & Not consider system delay and energy consumtion \\\midrule
				\cite{sun2024hierarchical} & MEC & Computation offloading and service caching & Minimize average service delay & MDP & hierarchical DRL & Not consider system energy consumtion \\\midrule
				\cite{wu2023computation} & SDN-based MEC & Stochastic game-based resource allocation & Minimize energy consumption and processing delay & MDP & MARL & Not consider tasks with maximum delay tolerance\\\midrule
				\cite{dai2020edge} & MEC & Resource allocation and computation offloading & Minimize energy consumption & MDP & DDPG & Not take user's deman into consideration \\\midrule
				\cite{liu2021learn} & MEC & Resource allocation and computation offloading & Minimize execution cost & POMDP & MADRL &  Not consider delay-sensitive tasks \\\midrule
				\cite{gong2022edge} & MEC-based IIoT & Resource allocation and computation offloading & Minimize task computation delay and energy consumption & MDP & DRL & Not take user's deman into consideration\\\midrule
				\cite{gao2022large} & Queuing-based heterogeneous MEC & Decentralized computation offloading & Optimize system cost and completion rates & MDP & Multi-agent DDPG & Not take user's deman into consideration \\\midrule
				\cite{9253665} &  Queuing-based MEC &  Computation offloading & Minimize drop rate and computation delay. & MDP & D3QN + LSTM & Not consider system energy consumtion\\\midrule
				\cite{wu2024combining} & Queuing-based IIoT MEC & Privacy aware computation offloading & Optimization of computation rate and energy consumption & MDP & DDPG  & Not take user's deman into consideration \\\midrule
				\cite{wu2023multi} & Queuing-based IIoT MEC & Computation offloading & Optimize delay and energy consumption & POMDP & Multi-agent DQN&  Not consider tasks with maximum delay tolerance \\\midrule
				\cite{huang2021deadline} & Queuing-based MEC & Computation offloading & Optimize drop rate and energy consumption & POMDP & DDPG & Not consider computation delay \\ \midrule
				\cite{Bolourian-WCL24} & Queuing-based MEC with EHs& Energy harvesting  computation offloading & Minimize drop rate and energy consumption. & MDP  & DQN & Not consider computation delay  \\\midrule
				QECO &  Queuing-based MEC &  Computation offloading & Maximize the QoE of each MD individually &MDP & D3QN + LSTM & \\
				\toprule
		\end{tabular}}
		\label{table1}}
\end{table*}

	\subsection{Motivation and Contributions}

	Although DRL-based methods have demonstrated their effectiveness in handling network dynamics, task offloading still encounters several challenges that require further attention.  \textcolor{blue}{As shown in Table~\ref{table1}, current research primarily focuses on minimizing energy consumption \cite{tang2022uav}, reducing processing delays \cite{guo2022energy}, \cite{seo2022differential}, maximizing computation rates~\cite{huang2019deep}, or optimizing a weighted balance among performance factors \cite{li2022joint}. However, QoE is a time-varying performance measure that reflects user satisfaction and is not affected only by delay, as considered in \cite{sun2024hierarchical}, \cite{9253665} but also by energy consumption \cite{Bolourian-WCL24}, \cite{huang2021deadline}. A more comprehensive approach is required to address the dynamic requirements of individual users in real-time scenarios with multiple MDs and ENs. 
		While some existing works such as \cite{liao2023online}, \cite{wu2024privacy}, \cite{dai2020edge}, \cite{gao2022large}, \cite{li2022joint} have investigated the trade-off between delay and energy consumption, they fail to address the user demands and fulfill QoE requirements properly.} In contrast to the aforementioned works, we propose a DRL-based distributed algorithm that provides users with an appropriate balance among QoE factors based on their demands. %We also explore a more realistic MEC scenario involving delay-sensitive tasks with processing deadlines, posing a more intricate challenge.

@@

\setcounter{section}{0}
\renewcommand*{\thesection}{\Roman{section}}
\makeatletter

\newpage

\section{Response to Reviewer 1}
\begin{enumerate}

\item \underline{Reviewer's Comment}: 
\textcolor{purple}{\textit{``(a) Lots of the studies focus on the research on resource optimisation of MEC by DRL, it is expected to survey the state-of-the-art within 3 years, and summarise it as an individual section, departing from the Section of Introduction. (b) Besides, the existing related work only has one paragraph without any discussion about the pros/cons of the previous work.''}} \newline

\underline{Authors' Reply}: (a) To address the reviewer comment about state-of-the-art within 3 years discusion, we have added this paragraph to the Section I, as follows. \newline
	\begin{my}{1cm}{1cm}
	\rev{\,\,\,\, To cope with the dynamic nature of the network, recent research has proposed several task offloading algorithms using machine learning methods. In particular, reinforcement learning (RL) hold promises to determine optimal decision-making policies by capturing the dynamics of environments and learning strategies for accomplishing long-term objectives \cite{arulkumaran2017deep}. RL can effectively tackle the challenges of MEC arising from the ever-changing nature of networks, MDs, and servers' heterogeneity. This ultimately improves the MD users' QoE. We explore state-of-the-art RL-based techniques characteristic to discuss how they address task offloading problems in MEC. To minimize energy consumption, Munir \textit{et al.} \cite{munir2021multi} developed a semi-distributed approach using a multi-agent RL (MARL) framework for self-powered MEC. Gong \textit{et al.} in \cite{gong2022edge} proposed a DRL-based network structure in the industrial IoT (IIoT) systems to jointly optimize task offloading and resource allocation to achieve lower energy consumption and decreased task delay. To investigate privacy aware computation offloading problem, Wu \textit{et al.} in \cite{wu2024combining} proposed a deep Q-network (DQN)-based method. They transform the problem on MDP to optimize computation rate and energy consumption in a queuing-based IIoT network. Sun \textit{et al.} in \cite{sun2024hierarchical} explored both computation offloading and service caching problems in MEC. They formulated an optimization problem that aims to minimize the long-term average service delay. They then proposed a hierarchical DRL framework, which effectively handles both problems under heterogeneous resources.}
\end{my}

\vspace{6mm}

(b) We have also revised the ralated works section, as below.\\
